### 2024-11-23 paper/dsl.tex
Add missing cref

% Relation definition
With relation, user can define the formal semantics of Wasm.
\cref{ex:dsl-testop} illustrates the execution semantics for \texttt{testop}
instruction described in a relation definition.
\\
\begin{example}
\begin{lstlisting}[style=dsl]
relation Step_pure: instr* ~> instr*
rule Step_pure/testop:
(CONST nt c_1) (TESTOP nt testop)  ~>  (CONST I32 c)
-- if c = @\dollarcode@testop_(nt, testop, c_1)
\end{lstlisting}
  \label{ex:dsl-testop}
\end{example}
The signature of the \texttt{Step\_pure} relation $\tildecode$\texttt{>} is
defined first.
A \texttt{Step\_pure} rule is then specified to describe the semantics of the
\texttt{testop} instruction with premises under which the relation holds.
SpecTec performs type checking to reject any incorrect symbols or ill-typed
relations like below codes.
\\
\begin{example}
\begin{lstlisting}[style=dsl]
(* Wrong type *)
rule Step_pure/testop:
(CONST nt c_1) (TESTOP nt testop)  ~>  c
-- if c = @\dollarcode@testop_(nt, testop, c_1)

@@

% Function definition
Functions enable auxiliary definitions that are used for other definitions such
as \texttt{\$testop\_} in the relation for \texttt{testop} in the code example
above.
As with relation definitions, defining a function begins by specifying the
signature of the function.
The function's actual definition is then specified, including output value and
the premises under which the function is applicable.
\cref{ex:dsl-fun} represents the function definition for \texttt{\$testop\_}.
% XXX: Hack
\newpage
\begin{example}
\begin{lstlisting}[style=dsl]
def @\dollarcode@testop_(nt, testop, num) : num
def @\dollarcode@testop_(nt, testop, c) = 1
-- if c = 0
def @\dollarcode@testop_(nt, testop, c) = 1
-- otherwise
\end{lstlisting}
  \label{ex:dsl-fun}
\end{example}
In addition, functions themselves can be used to describe semantics, rather
than merely serving as auxiliary definitions.
Specifically, SpecTec employs function definitions to describe semantics of module
instantiation and function invocation.

>>>>

% Relation definition
With relation, user can define the formal semantics of Wasm.
\cref{ex:dsl-testop} illustrates the execution semantics for \texttt{testop}
instruction described in a relation definition.
\\
\begin{example}
\begin{lstlisting}[style=dsl]
relation Step_pure: instr* ~> instr*
rule Step_pure/testop:
(CONST nt c_1) (TESTOP nt testop)  ~>  (CONST I32 c)
-- if c = @\dollarcode@testop_(nt, testop, c_1)
\end{lstlisting}
  \label{ex:dsl-testop}
\end{example}
The signature of the \texttt{Step\_pure} relation $\tildecode$\texttt{>} is
defined first.
A \texttt{Step\_pure} rule is then specified to describe the semantics of the
\texttt{testop} instruction with premises under which the relation holds.
SpecTec performs type checking to reject any incorrect symbols or ill-typed
relations like \cref{ex:dsl-error}.
\\
\begin{example}
\begin{lstlisting}[style=dsl]
(* Wrong type *)
rule Step_pure/testop:
(CONST nt c_1) (TESTOP nt testop)  ~>  c
-- if c = @\dollarcode@testop_(nt, testop, c_1)

@@

% Function definition
Functions enable auxiliary definitions that are used for other definitions such
as \texttt{\$testop\_} in the premise of \cref{ex:dsl-testop}.
As with relation definitions, defining a function begins by specifying the
signature of the function.
The function's actual definition is then specified, including output value and
the premises under which the function is applicable.
\cref{ex:dsl-fun} represents the function definition for \texttt{\$testop\_}.
% XXX: Hack
\newpage
\begin{example}
\begin{lstlisting}[style=dsl]
def @\dollarcode@testop_(nt, testop, num) : num
def @\dollarcode@testop_(nt, testop, c) = 1
-- if c = 0
def @\dollarcode@testop_(nt, testop, c) = 1
-- otherwise
\end{lstlisting}
  \label{ex:dsl-fun}
\end{example}
In addition, functions themselves can be used to describe semantics, rather
than merely serving as auxiliary definitions.
Specifically, SpecTec employs function definitions to describe semantics of module
instantiation and function invocation.
